Chemical tagging can work: \\ Identification of stellar phase-space structures \\ purely by chemical-abundance similarity\vspace{-7ex}

### 2016-08-24 papers/kmeans/kmeans.tex
update to pdf figures
back off slightly on density wording

% figure 
\newlength{\figwidth}\setlength{\figwidth}{0.3\textwidth}
\newcommand{\insanefigure}[1]{\rule{0ex}{\headsep}\\% This shouldn't be necessary, but something is fucked with AASTEX 6.0
\includegraphics[width=\figwidth]{./figs/#1_MgFe.png}%
\includegraphics[width=\figwidth]{./figs/#1_MgK.png}%
\includegraphics[width=\figwidth]{./figs/#1_AlMg.png}\\
\includegraphics[width=\figwidth]{./figs/#1_NaO.png}%
\includegraphics[width=\figwidth]{./figs/#1_CN.png}%
\includegraphics[width=\figwidth]{./figs/#1_SAl.png}\\
\includegraphics[width=2\figwidth]{./figs/#1_gal.png}%
\includegraphics[width=\figwidth]{./figs/#1_HR.png}\\
\includegraphics[width=2\figwidth]{./figs/#1_vlon.png}%
\includegraphics[width=\figwidth]{./figs/#1_context.png}}

@@

When the k-means results are returned, the $D\times D$ empirical
variance tensor for the members of each cluster can be constructed.
From this, an effective density in the abundance space can be computed
as the number of points in the cluster divided by the square-root of
the determinant of the tensor.
This density was used to rank abundance-space overdensities (from highest
to lowest) for visual inspection.
In \figurename~\ref{fig:densities} we show the distribution of cluster membership
and density for the $K=256$ run of k-means.
The densest clusters tend to have fewer members, presumably because
the bulk of the population is not extremely strongly clustered, or not
in ways to which k-means is sensitive.

Importantly, the k-means algorithm assigns \emph{every} star to at
least one cluster.
For this reason, there is no sense in which \emph{every} ``cluster'' returned
by k-means is a distinct overdensity in abundance space.
In what follows, we only consider high-density clusters---clusters
that are much more dense than average; these ought to represent true
over-densities in abundance space.

@@

The abundance-space clusters shown in the \figurename s
might not look dense in 2-d projections of the abundance space, but they
are very dense in the 15-dimensional space.  Indeed,
\figurename~\ref{fig:M13} is the densest cluster found in the 15-d
space \emph{by far}.
The challenge of this work is to find structure in the high
dimensionality space that is not obviously visible in any 2-d projection.
Although we have by no means any model of the 15-d space, we do know
that the structures shown in the \figurename s are very high in 15-d
density.

@@

\begin{figure}[!bp]
\includegraphics[width=1.5\figwidth]{./figs/clusters_0256.png}
\caption{The distribution of membership and density for the 256
  abundance-space clusters returned by the k-means algorithm at
  $K=256$.  The densest cluster (which is displayed in more detail in 
  \figurename~\ref{fig:M13}) is far more dense than the second
  densest.\label{fig:densities}}
\end{figure}
\begin{figure}[!p]
\insanefigure{cluster_0256_0253}
\caption{Same as \figurename~\ref{fig:all} except that the entire
  sample has been made gray and the members of the most dense $K=256$
  abundance-space cluster have been rendered as unique, prominent
  triangles (color is velocity rank, orientation is $\logg$ rank).
  The lower-right plot shows this cluster (circle) in context of the
  other clusters (dots).  This cluster, which was identified only in
  abundance space (six projections of which are the top six panels in
  this \figurename), turns out to be dominated by the halo globular
  cluster M13. The symbol orientations and colors have no meaning;
  they are randomly generated---one unique color and orientation for
  each highlighted star---to make the points cross-identifiable across
  panels.\label{fig:M13}}
\end{figure}
\begin{figure}[!p]
\insanefigure{cluster_0256_0034}
\caption{Same as \figurename~\ref{fig:M13} but for another dense
  abundance-space cluster.
  This one turns out to be dominated by globular
  cluster M5.\label{fig:M5}}
\end{figure}
\begin{figure}[!p]
\insanefigure{cluster_0256_0177}
\caption{Same as \figurename~\ref{fig:M13} but for another dense
  abundance-space cluster.
  This one turns out to be dominated by the Sagittarius dwarf spheroidal galaxy.\label{fig:Sgr}}
\end{figure}
\begin{figure}[!p]
\insanefigure{cluster_0256_0010}
\caption{Same as \figurename~\ref{fig:M13} but for another dense
  abundance-space cluster.
  This one turns out to be dominated by a hitherto unrecognized high-velocity-dispersion
  structure in the Galaxy halo.\label{fig:halo}}
\end{figure}
\begin{figure}[!p]
\insanefigure{cluster_0256_0141}
\caption{Same as \figurename~\ref{fig:M13} but for another dense
  abundance-space cluster.
  This one turns out to be dominated by a very thin young stellar
  structure in the Galaxy disk, probably one that has been discovered previously \citep{wegg}.\label{fig:disk}}
\end{figure}

>>>>

% figure 
\newlength{\figwidth}\setlength{\figwidth}{0.3\textwidth}
\newcommand{\insanefigure}[1]{\rule{0ex}{\headsep}\\% This shouldn't be necessary, but something is fucked with AASTEX 6.0
\includegraphics[width=\figwidth]{./figs/#1_MgFe.pdf}%
\includegraphics[width=\figwidth]{./figs/#1_MgK.pdf}%
\includegraphics[width=\figwidth]{./figs/#1_AlMg.pdf}\\
\includegraphics[width=\figwidth]{./figs/#1_NaO.pdf}%
\includegraphics[width=\figwidth]{./figs/#1_CN.pdf}%
\includegraphics[width=\figwidth]{./figs/#1_SAl.pdf}\\
\includegraphics[width=2\figwidth]{./figs/#1_gal.pdf}%
\includegraphics[width=\figwidth]{./figs/#1_HR.pdf}\\
\includegraphics[width=2\figwidth]{./figs/#1_vlon.pdf}%
\includegraphics[width=\figwidth]{./figs/#1_context.pdf}}

@@

When the k-means results are returned, the $D\times D$ empirical
variance tensor for the members of each cluster can be constructed.
From this, an effective density in the abundance space can be computed
as the number of points in the cluster divided by the square-root of
the determinant of the tensor.
This density was used to rank abundance-space overdensities (from highest
to lowest) for visual inspection.
In \figurename~\ref{fig:densities} we show the distribution of cluster membership
and density for the $K=256$ run of k-means.

Importantly, the k-means algorithm assigns \emph{every} star to at
least one cluster.
For this reason, there is no sense in which \emph{every} ``cluster'' returned
by k-means is a distinct overdensity in abundance space.
In what follows, we only consider high-density clusters---clusters
that are more dense than average for their occupation number (total membership); these ought to represent true
over-densities in abundance space.

@@

The abundance-space clusters shown in the \figurename s
might not look dense in 2-d projections of the abundance space, but they
are very dense in the 15-dimensional space.  Indeed,
\figurename~\ref{fig:M13} is the densest cluster found in the 15-d
space \emph{by far}.
The challenge of this work is to find structure in the high
dimensionality space that is not obviously visible in any 2-d projection.
Although we have by no means any model of the 15-d space, we do know
that the structures shown in the \figurename s are high in 15-d
density, or at least relative to other clusters with the same occupation number.

@@

\begin{figure}[!bp]
\includegraphics[width=1.5\figwidth]{./figs/clusters_0256.pdf}
\caption{The distribution of membership and density for the 256
  abundance-space clusters returned by the k-means algorithm at
  $K=256$.  The densest cluster (which is displayed in more detail in 
  \figurename~\ref{fig:M13}) is far more dense than the second
  densest.\label{fig:densities}}
\end{figure}
\begin{figure}[!p]
\insanefigure{cluster_0256_0253}
\caption{Same as \figurename~\ref{fig:all} except that the entire
  sample has been made gray and the members of the most dense $K=256$
  abundance-space cluster have been rendered as unique, prominent
  triangles (color is velocity rank, orientation is $\logg$ rank).
  The lower-right plot shows this cluster (circle) in context of the
  other clusters (dots).  This cluster, which was identified only in
  abundance space (six projections of which are the top six panels in
  this \figurename), turns out to be dominated by the halo globular
  cluster M13. The symbol orientations and colors have no meaning;
  they are randomly generated---one unique color and orientation for
  each highlighted star---to make the points cross-identifiable across
  panels.\label{fig:M13}}
\end{figure}
\begin{figure}[!p]
\insanefigure{cluster_0256_0034}
\caption{Same as \figurename~\ref{fig:M13} but for another dense
  abundance-space cluster.
  This one turns out to be dominated by globular
  cluster M5.\label{fig:M5}}
\end{figure}
\begin{figure}[!p]
\insanefigure{cluster_0256_0177}
\caption{Same as \figurename~\ref{fig:M13} but for another dense
  abundance-space cluster.
  This one turns out to be dominated by the Sagittarius dwarf spheroidal galaxy.\label{fig:Sgr}}
\end{figure}
\begin{figure}[!p]
\insanefigure{cluster_0256_0010}
\caption{Same as \figurename~\ref{fig:M13} but for another dense
  abundance-space cluster.
  This one turns out to be dominated by a hitherto unrecognized high-velocity-dispersion
  structure in the Galaxy halo.\label{fig:halo}}
\end{figure}
\begin{figure}[!p]
\insanefigure{cluster_0256_0141}
\caption{Same as \figurename~\ref{fig:M13} but for another dense
  abundance-space cluster.
  This one turns out to be dominated by a very thin young stellar
  structure in the Galaxy disk, probably one that has been discovered previously \citep{wegg}.\label{fig:disk}}
\end{figure}
